Constant-round Blind Classical Verification of Quantum Sampling

### 2020-09-04 qpip0.tex
Fix typo

We now decompose the prover's internal state by using \Cref{lem:partition2} iteratively.
Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define
\begin{equation}
	\Cref{eq:partition-string}
	\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.
\end{equation}

For all $i\in[m]$, we decompose
	$$\ket{\psi}=\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}$$
where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.

>>>>

We now decompose the prover's internal state by using \Cref{lem:partition2} iteratively.
Let $\ket{\psi}$ be the state the prover holds before he receives $\vec{c}$;
we denote the corresponding Hilbert space as $H_{\regX,\regZ}$.
For all $k\leq m$, $d\in \zo^k$, $\gamma=(\gamma_1, \ldots, \gamma_k)$ where each $\gamma_j\in\set{\frac{\gamma_0}{T},\frac{2\gamma_0}{T},\dots,\frac{T\gamma_0}{T}}$ \Ethan{This ok?}, and $\ket{\psi} \in H_{\regX,\regZ}$, define $$\ket{\psi_{d,\gamma}}\defeq G_{d_k,k,\gamma_k}\ldots G_{d_2,2,\gamma_2} G_{d_1,1,\gamma_1} \ket{\psi}.$$
For all $i\in[m]$, we then decompose
\begin{equation}
	\label{eq:partition-string}
	\ket{\psi}=\sum_{j=0}^{i-1} \ket{\psi_{1^j0,\gamma}} +\ket{\psi_{1^i,\gamma}} +\sum_{j=1}^{i}\ket{\psi_{err,j,\gamma}}
\end{equation}
where $\ket{\psi_{err,i,\gamma}}$ denotes the error state from decomposing $\ket{\psi_{1^{i-1},\gamma}}$.
